Requirements and Current State of Knowledge Representation Systems for Service Robotics

### 2012-04-24 krs-survey.tex
Added references to Soar

While classical cognitive architectures like {\sc Soar} or {\sc ACT-R} have
declarative knowledge modules~\cite{Derbinsky2010} and have been recently used
on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for instance), they are
also absent from this survey because we did not find much references in the
literature on knowledge manipulation and representation applied to robotic
scenarii in these architectures.

@@

>>>>

While classical cognitive architectures like {\sc Soar}~\cite{Lehman2006} or
{\sc ACT-R} have declarative knowledge modules~\cite{Derbinsky2010} and have
been recently used on service robots (see {\sc ACT-R/E}~\cite{Kennedy2009} for
instance), they are also absent from this survey because we did not find much
references in the literature on knowledge manipulation and representation
applied to robotic scenarii in these architectures.

@@

In the larger field of cognitive architectures, the {\sc Soar}
architecture~\cite{Lehman2006} is one of those that tries to reproduce a
human-like memory organization.
